%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Stylish Resume
% LaTeX Template
% Version 1.0 (18/7/12)
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{../resume} 

\author{Caleb Thorsteinson}

\primarycolor{1b054c}
\accentcolor{118aa3}

\phone{(999)-999-9999}
\email{caleb@thorsteinson.io}
\linkedin{thorsteinson}
\address{Seattle, WA}
\university{University of Washington}{September 2012}{June 2016}{B.S. Informatics}
\github{thorsteinson}

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{employer}[../microsoft]{Microsoft} {August 2016}{April 2019}
  {Technical Program Manager}
\begin{team}{Ambient Computing and Robotics}{Internship}
  Developed a generic object storage system for tagging and labelling
  video footage with Python, OpenCV, and HDF5. Applied scientists on
  the team used this for training a computer vision model that
  provided real time tracking of people and objects in an environment.
\end{team}
\begin{team}{Dynamics 365 LinkedIn Integration}{}
  Shipped several major feature updates to the Dynamics 365 LinkedIn
  Sales Navigator integration, including a responsive org
  chart. Facilitated relationship with LinkedIn to integrate new
  features and beat competetitors to market. Worked with engineering
  and design to creatively satisfy customer requests.
\end{team}
\begin{team}{Sales Intelligence}{}
  Shipped an internal webapp for Account Executives that curated AI
  and automated sales reccomendations. Worked closely with
  stakeholders across multiple teams at Microsoft to pool data from
  unrelated systems. Managed feature requests from internal
  stakeholders that balanced customer priority and technical dept. Ran
  SCRUM meetings to drive progress and unblock scientists or engineers
  as issues arised. Executed plan for achieving GDPR compliance over
  two month period.  % MS SQL % Azure Data Lake Storage
\end{team}
\begin{team}{Gigjam}{}
  Gigjam was a cross platform application that allowed different types
  of documents to be shared, and collaboratively edited in a single
  workspace. The redaction feature allowed users to include or exclude
  certain parts of documents before they were shared. I collaborated
  with the design and engineering teams to ship two major
  enhancements. One was auto redaction, which would automatically
  redact personal information. The other was image redaction, which
  gave users the ability to exclude a part of a image. Mended
  relations between the design and engineering team so they could
  easily collaborate and execture more quickly.
\end{team}
\end{employer}

\newcolumn

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\section{Skills}

\begin{skilltable}{Langauges}
  \skill{Python}{4}
  \skill{Go}{4}
  \skill{Java}{3}
  \skill{Haskell}{3}
  \skill{JavaScript}{3}
  \skill{Bash}{1}
  \skill{Powershell}{1}
\end{skilltable}

\begin{skilltable}{Tools}
  \skill{Git}{4}
  \skill{Linux}{4}
  \skill{Sql}{3}
  \skill{Azure}{3}
\end{skilltable}

\begin{skilltable}{Theory}
  \skill{UX}{3}
  \skill{Algorithms}{3}
  \skill{Architecture}{2}
\end{skilltable}
    
\end{document}
